Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-02 R0V0.tex
Address the comment on the last Ian's review.
Write the matrix W computed for the example

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system:differential}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

	The MI \eqref{eq:MI formulation} implies that the inequality
	\begin{equation*}
		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
	\end{equation*}
	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds. Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.

@@

	\item If the matrices $W_1,\ldots,W_N$ belong to $T$, then a solution has been found and the algorithm can be stopped. Otherwise, solve the global problem
	\begin{equation*}
		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i+\Lambda_i^k\right|\right|_F^2\;;
	\end{equation*}
	\item Update $\Lambda$ and return to step 1
	\begin{equation*}
		\Lambda_i^{k+1}=Q_{W_i}^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
	\end{equation*}
\end{enumerate}
Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $Q_{W_i}$ and the values $\Lambda_i$.

\mypara As $k\to\infty$, for each index $i\in\mathbb{N}_{[1,N]}$, the Gramians $Q_{W_i}$ will coincide with the matrices $Z_i$. Consequently, the block-diagonal matrix $Z$ is symmetric and positive definite. Thus, $p_{MI}\in\mathbb{SOS}[x,v]$ and, for each index $i\in\mathbb{N}_{[1,N]}$, $v_i^\top W_iv_i\in\mathbb{SOS}[x_i,v_i]$. Hence, $M=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)^{-1}$ is a separable control contraction metric for system \eqref{eq:general system}.

@@

>>>>

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

\mypara The existence of a control contraction metric for system~\eqref{eq:general system} implies that there exist matrices $(W,Y)$ that are a solution to the MI~\eqref{eq:MI formulation} with structure prescribed by the set $\Xi$.

@@

\mypara	The MI \eqref{eq:MI formulation} implies that the inequality
	\begin{equation*}
		\delta_x^\top\bigg(\dot{M}+(A+BK)M+M(A+BK)^\top-2\lambda M\bigg)\delta_x\leq0
	\end{equation*}
	holds, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the condition defined by the set of equations \eqref{eq:Arstein-Sontag} holds. Thus, $M$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and, according to Theorem~\ref{prop:CCM Existence}, \eqref{eq:differential feedback law} is a differential feedback rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop.

@@

	\item If the matrices $W_1,\ldots,W_N$ belong to $T$, then a solution has been found and the algorithm can be stopped. Otherwise, solve the global problem
	\begin{equation*}
		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|Q_{W_i}^{k+1}-Z_i-\Lambda_i^k\right|\right|_F^2\;;
	\end{equation*}
	\item Update $\Lambda$ and return to step 1
	\begin{equation*}
		\Lambda_i^{k+1}=Q_{W_i}^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
	\end{equation*}
\end{enumerate}
Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $Q_{W_i}$ and the values $\Lambda_i$.

\mypara As $k\to\infty$, for each index $i\in\mathbb{N}_{[1,N]}$, the Gramians $Q_{W_i}$ will coincide with the matrices $Z_i$. Consequently, the block-diagonal matrix $Z$ is symmetric and positive semidefinite. Thus, $p_{MI}\in\mathbb{SOS}[x,v]$ and, for each index $i\in\mathbb{N}_{[1,N]}$, $v_i^\top W_iv_i\in\mathbb{SOS}[x_i,v_i]$. Hence, $M=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)^{-1}$ is a separable control contraction metric for system \eqref{eq:general system}.

@@

\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} leads to the following components of the matrix $W$ for system~\eqref{eq:example} with four agents lead to the

\begin{figure*}
\begin{align*}
	W_1(q_1)=1\times10^{-7}\begin{bmatrix}
	18-15x_1-28y_1+11.2y_1^2+3.2x_1^2+1.2x_1y_2&9.3+35x_1-43y_1+28y_1^2-16x_1^2-16x_1y_1\\
	*&4.9+40x_1-37y_1+72y_1^2+84x_1^2-155x_1y_1
	\end{bmatrix}\;,\\
	W_2(q_2)=1\times10^{-7}\begin{bmatrix}1-3.7x_2+2.3y_2+1.3y_2^2+3.5x_2^2-4.3x_2y_2&
	-0.6-0.6x_2+y_2+2y_2^2+3.5x_2^2-5.5x_2y_2\\
	*&0.4+2.3x_2-2.3y_2+3.3y_2^2+3.4x_2^2-6.7x_2y_2
	\end{bmatrix}\;,\\
	W_3(q_3)=1\times10^{-7}\begin{bmatrix}
		127-248x_3+18y_3+y_3^2+122x_3^2-18x_3y_3&
		-98+146x_3+19y_3+1.9y_3^2-50x_3^2-22x_3y_3\\
		*&76-78x_3-42y_3+6.4y3^2+21x_3^2+20x_3y_3
	\end{bmatrix}\;,\\
	W_4(q_4)=1\times10^{-6}\begin{bmatrix}
	22+4x_4-17y_4+8.8y_4^2+9.4x_4^2+12x_4y_4&
	-8.6-5.9x_4+1.8y_4-4.2y_4^2-9.7x_4^2-12x_4y_4\\
	*&4.3+7.5x_4+2.8y_4+3.2y_4^2+10x_4^2+11x_4y_4
	\end{bmatrix}\;.
\end{align*}
\end{figure*}
